---
title: "ADNI Project"
author: "Soham Dighe"
date: '2022-09-26'
output: pdf_document
---

```{r setup, include=FALSE}
library(MASS)
library(ISLR)
library(corrplot)
library(glmnet)
library(HRW)
library(knitr)
library(formatR)
library(gam)
library(splines)
library(locfit)
library(plot.matrix)
library(png)
library(tableone)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 80), tidy = TRUE)
```

# Analysis of our datasets 

## Checking if the difference in age is significant
```{r}
control = read.csv(file = '/Users/sohamdighe/Documents/SCIE90017/Data/ADNI/control.csv')
diabetes = read.csv(file = '/Users/sohamdighe/Documents/SCIE90017/Data/ADNI/diabetes.csv')
control$DX = as.factor(control$DX)
control$APOE4 = as.factor(control$APOE4)
control$ABETA = as.numeric(control$ABETA)
control$PTGENDER = as.factor(control$PTGENDER)
control$PTETHCAT = as.factor(control$PTETHCAT)
control$PTRACCAT = as.factor(control$PTRACCAT)

diabetes$DX = as.factor(diabetes$DX)
diabetes$APOE4 = as.factor(diabetes$APOE4)
diabetes$ABETA = as.numeric(diabetes$ABETA)
diabetes$PTGENDER = as.factor(diabetes$PTGENDER)
diabetes$PTETHCAT = as.factor(diabetes$PTETHCAT)
diabetes$PTRACCAT = as.factor(diabetes$PTRACCAT)
diabetes$PTAU = as.numeric(diabetes$PTAU)
plot(y = control$AGE,x = control$DX,xlab = 'Diagnosis',ylab ='Age of patient')
plot(y = diabetes$AGE,x = diabetes$DX,xlab = 'Diagnosis',ylab='Age of patient')
```

Checking normality of age through Shapiro-Wilk test
```{r}
shapiro.test(control$AGE)
shapiro.test(diabetes$AGE)
# trying to plot the data anyways
qqnorm(control$AGE)
qqline(control$AGE)
qqnorm(diabetes$AGE)
qqline(diabetes$AGE)
```

Now, we have established both are normally distributed so we will do t test on them.
```{r}
t.test(control$AGE,diabetes$AGE)
```
From the above test we reject the alternativce hypothesis and hence the true difference between means is zero and hence is not statistically significant.
```{r,include=FALSE}
writeLines(diabetes$PTID)
writeLines(control$PTID)
```
\newpage

## Table 1

Here, we have a caveat. We still have not replaced missing data in the files so the values are not final but should give a decent estimate. FDG,PIB,FBB,AV45 and CSF markers are the ones with most null values. This is still to be addressed. 
```{r,warning=FALSE}
variables_selected = c('AGE','MMSE','CDRSB','FDG','PIB','AV45','PTGENDER','PTEDUCAT','PTETHCAT','PTRACCAT','APOE4','ABETA','PTAU','TAU','Ventricles','Hippocampus','mPACCdigit','mPACCtrailsB')
control_tab <- CreateTableOne(vars = variables_selected,data = control,strata = "DX")
control_tab
diabetes_tab <- CreateTableOne(vars = variables_selected,data = diabetes,strata = "DX")
diabetes_tab
```

```{r,warning=FALSE}
cohort = rbind(control,diabetes)
tab <- CreateTableOne(vars = variables_selected,data = cohort,strata = "DX")
tab
```